Paper Plots V6

### 2025-06-10 Rmd/paper_plots/paper_plots_1.6.Rmd
include more scenarios and plot scripts

---
title: "Paper Plots V5"
author: "Brett Stacy"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

@@

@@

plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3) 
text(1977, 420000, "B")
mtext("Year", side = 1, line = 2, cex = 1.5)

# compare with and without SS
par(mfrow = c(1,1))
plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss, type = "o", pch = 19, ylab = "ISSB", ylim = c(0, 15000), cex.lab = 1.3) 
lines(out_1.4.old$length$iss$YEAR, out_1.4.old$length$iss$iss, col = "blue", type = "o", pch = 5)
legend(1977, 11000, lty = c(1,1), col = c("black", "blue"), pch = c(19, 5), legend = c("Not including sampling strata weighting", "Including sampling strata weighting"), bty = "n")

@@

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(3,1), mar = c(0,3.1,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss, type = "o", pch = 19, ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.5, cex.axis = 1.3)
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue", type = "o", pch = 3)
lines(out_1.5$length$iss$YEAR, out_1.5$length$iss$nhls, col = "orange", type = "o", 5)
legend(1977, 11000, lty = c(1,1,1), col = c("black", "blue", "orange"), pch = c(19, 3, 5), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n", cex = 1.5)
text(1977, 14000, "A", cex = 1.5)

plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xaxt = "n", cex.lab = 1.5, cex.axis = 1.3)
text(1977, 420000, "B", cex = 1.5)

plot(out_5.2$length$iss$YEAR[sub_range], out_5.2$length$iss$iss[sub_range], ylab = "ISSB", cex.lab = 1.5, col = "cyan", ylim = c(0, 27000), xlab = "", xaxt = "n", lwd = 1.5, type = "o", pch= 18, cex.axis = 1.3)
axis(side = 1, at = seq(1980, 2020, by = 5), cex.axis = 1.3)
lines(out_9.2$length$iss$YEAR[sub_range], out_9.2$length$iss$iss[sub_range], type = "o", pch = 15, col = "orange3", lwd = 1.5)
lines(out_4.2$length$iss$YEAR[sub_range], out_4.2$length$iss$iss[sub_range], type = "o", pch = 17, col = "magenta", lwd = 1.5)
lines(out_1.5$length$iss$YEAR[sub_range], out_1.5$length$iss$iss[sub_range], type = "o", pch = 19, col = "black", lwd = 1.5, lty = 1)
legend(1977, 20000, title = "Scenario", legend = c("1", "2", "3", "Full"), lty = c(1,1,1,1), pch = c(18, 15, 17, 19), col = c("cyan", "orange3", "magenta", "black"), bty = "n", lwd = rep(1.5, 4), cex = 1.5)
text(1977, 23000, "C", cex = 1.5)

@@

```{r, fig.height=10}
out_1.5$length$og_props %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
  geom_line() +
  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
  # geom_area_pattern(aes(pattern = Year, y = og_FREQ, x = LENGTH), alpha = 0.5, position = "identity") +
  theme_classic() +
  scale_x_continuous(limits = c(22, 108),
                     n.breaks = 9) +
  labs(x = "Length (cm)", y = "Frequency", tag = "A") +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  scale_y_continuous(limits = c(0, .04), expand = c(0, 0)) +
  scale_color_viridis_d() +
  scale_fill_viridis_d()

@@

p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "E") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_1.5$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

@@

p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "B") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_5.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

@@

p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "C") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_9.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

@@

p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "D") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_4.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(2,2)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# # now do RSS with boot all + SS
# out_2.2$length$rss %>% 
#   tidytable::filter(YEAR %in% 2003:2004) %>% 
#   tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
# 
# p3.5 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
#   geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
#   theme_classic() +
#   theme(legend.position = c(0.8, 0.8),
#         plot.tag.position = c(0.1, 0.95),
#         plot.tag = element_text(size = 14, face = "bold")) +
#   labs(x = "RSS", y = "Count", tag = "E") + 
#   geom_point(data = props.sub %>% 
#                tidytable::left_join(out_2.2$length$iss %>% 
#                                       tidytable::select(YEAR, iss)) %>% 
#                tidytable::summarise(x = unique(iss), .by = Year) %>% 
#                # tidytable::summarise(x = median(rss), .by = Year) %>% 
#                tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
#   scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
#   # scale_x_continuous(n.breaks = 8)
#   scale_x_continuous(breaks = seq(0, 35000, by = 2500),
#                      labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
#                      limits = c(0, 35000),
#                      expand = c(0, 0))
# 
#

# 
# p1 / p3
# p1 / p3 / p3.2

@@

# * Time series Expansion NEW
```{r, fig.width=9, fig.height=5}
out_2.1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_44.1_ISS_500_iters_2025-03-25.RDS")

>>>>

---
title: "Paper Plots V6"
author: "Brett Stacy"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

@@

assessment_2023_iss_FI = tidytable(year = 1999:2023,
                                iss = c(2078,
                                        1396,
                                        1829,
                                        2159,
                                        1040,
                                        1887,
                                        1164,
                                        2487,
                                        270,
                                        1757,
                                        908,
                                        1191,
                                        1398,
                                        865,
                                        909,
                                        1057,
                                        2068,
                                        3149,
                                        2802,
                                        2996,
                                        1230,
                                        0,
                                        3167,
                                        2388,
                                        1976))

@@

plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3) 
text(1977, 420000, "B")
mtext("Year", side = 1, line = 2, cex = 1.5)
```

```{r, fig.height=6}
# compare with and without SS
par(mfrow = c(1,1))
plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss, type = "o", pch = 19, ylab = "ISSB", ylim = c(0, 13000), cex.lab = 1.3) 
lines(out_1.4.old$length$iss$YEAR, out_1.4.old$length$iss$iss, col = "blue", type = "o", pch = 5)
legend(1977, 11000, lty = c(1,1), col = c("black", "blue"), pch = c(19, 5), legend = c("Not including sampling strata weighting", "Including sampling strata weighting"), bty = "n")

@@

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(3,1), mar = c(0,3.2,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss, type = "o", pch = 19, ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.5, cex.axis = 1.3)
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue", type = "o", pch = 3)
lines(out_1.5$length$iss$YEAR, out_1.5$length$iss$nhls, col = "orange", type = "o", 5)
legend(1977, 11000, lty = c(1,1,1), col = c("black", "blue", "orange"), pch = c(19, 3, 5), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n", cex = 1.5)
text(1977, 14000, "a", cex = 2, font = 2)

plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xaxt = "n", cex.lab = 1.5, cex.axis = 1.3)
text(1977, 420000, "b", cex = 2, font = 2)

plot(out_5.2$length$iss$YEAR[sub_range], out_5.2$length$iss$iss[sub_range], ylab = "ISSB", cex.lab = 1.5, col = "cyan", ylim = c(0, 26000), xlab = "", xaxt = "n", lwd = 1.5, type = "o", pch= 18, cex.axis = 1.3)
axis(side = 1, at = seq(1980, 2020, by = 5), cex.axis = 1.3)
lines(out_9.2$length$iss$YEAR[sub_range], out_9.2$length$iss$iss[sub_range], type = "o", pch = 15, col = "orange3", lwd = 1.5)
lines(out_4.2$length$iss$YEAR[sub_range], out_4.2$length$iss$iss[sub_range], type = "o", pch = 17, col = "magenta", lwd = 1.5)
lines(out_1.5$length$iss$YEAR[sub_range], out_1.5$length$iss$iss[sub_range], type = "o", pch = 19, col = "black", lwd = 1.5, lty = 1)
legend(1977, 20000, title = "Scenario", legend = c("1", "2", "3", "Full"), lty = c(1,1,1,1), pch = c(18, 15, 17, 19), col = c("cyan", "orange3", "magenta", "black"), bty = "n", lwd = rep(1.5, 4), cex = 1.5)
text(1977, 23000, "c", cex = 2, font = 2)

@@

```{r, fig.height=9}
out_1.5$length$og_props %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
  geom_line() +
  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
  # geom_area_pattern(aes(pattern = Year, y = og_FREQ, x = LENGTH), alpha = 0.5, position = "identity") +
  theme_classic() +
  scale_x_continuous(limits = c(22, 108),
                     n.breaks = 9) +
  labs(x = "Length (cm)", y = "Frequency", tag = "a") +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  scale_y_continuous(limits = c(0, .04), expand = c(0, 0)) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2")

@@

p3 = ggplot(data = props.sub, aes(x = rss, colour = Year, shape = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "e") +
  geom_point(data = props.sub %>%
               tidytable::left_join(out_1.5$length$iss %>%
                                      tidytable::select(YEAR, iss)) %>%
               tidytable::summarise(x = unique(iss), .by = Year) %>%
               # tidytable::summarise(x = median(rss), .by = Year) %>%
               tidytable::mutate(y = c(5,6)), aes(x,y, fill = Year, color = Year), size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  scale_shape_manual(values = c(23, 25)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", ""),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2")

@@

p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year, shape = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "b") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_5.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(7,9)), aes(x,y, fill = Year, color = Year), size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
  scale_shape_manual(values = c(23, 25)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", ""),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2")

@@

p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year, shape = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "c") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_9.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(5,6)), aes(x,y, fill = Year, color = Year), size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  scale_shape_manual(values = c(23, 25)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", ""),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2")

@@

p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year, shape = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "d") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_4.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(2,2)), aes(x,y, fill = Year, color = Year), size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
  scale_shape_manual(values = c(23, 25)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", ""),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2")

@@

# * 2000 & 2001 Histograms

```{r, fig.height=10}
out_1.5$length$og_props %>% 
  tidytable::filter(YEAR %in% 2000:2001) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
  geom_line() +
  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
  # geom_area_pattern(aes(pattern = Year, y = og_FREQ, x = LENGTH), alpha = 0.5, position = "identity") +
  theme_classic() +
  scale_x_continuous(limits = c(22, 108),
                     n.breaks = 9) +
  labs(x = "Length (cm)", y = "Frequency", tag = "a") +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  scale_y_continuous(limits = c(0, .04), expand = c(0, 0)) +
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS
out_1.5$length$rss %>% 
  tidytable::filter(YEAR %in% 2000:2001) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 100) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "e") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_1.5$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS with boot_length only.
out_5.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2000:2001) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "b") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_5.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS with boot_length and boot_haul.
out_9.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2000:2001) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "c") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_9.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS with boot all.
out_4.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2000:2001) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "d") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_4.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(2,2)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# * 1998 & 1999 Histograms

```{r, fig.height=10}
out_1.5$length$og_props %>% 
  tidytable::filter(YEAR %in% 1998:1999) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
  geom_line() +
  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
  # geom_area_pattern(aes(pattern = Year, y = og_FREQ, x = LENGTH), alpha = 0.5, position = "identity") +
  theme_classic() +
  scale_x_continuous(limits = c(22, 108),
                     n.breaks = 9) +
  labs(x = "Length (cm)", y = "Frequency", tag = "a") +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  scale_y_continuous(limits = c(0, .04), expand = c(0, 0)) +
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS
out_1.5$length$rss %>% 
  tidytable::filter(YEAR %in% 1998:1999) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 100) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "e") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_1.5$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS with boot_length only.
out_5.2$length$rss %>% 
  tidytable::filter(YEAR %in% 1998:1999) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "b") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_5.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS with boot_length and boot_haul.
out_9.2$length$rss %>% 
  tidytable::filter(YEAR %in% 1998:1999) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "c") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_9.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS with boot all.
out_4.2$length$rss %>% 
  tidytable::filter(YEAR %in% 1998:1999) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
